Interval Probability for Fuzzy Quantum Theories

### 2016-07-15 prob.tex
prob.tex Updated relating to the Radon-Nikodym theorem...

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}

@@

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by 
\begin{equation}
\pmeas(E)=\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in E}}\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $\rho:\Omega\rightarrow[0,1]$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in\Omega}}\rho(\omega)=1$.
Furthermore, every probability measure~$\pmeas$ can be written in
this form for an unique $\rho$~\cite{Kolmogorov1950,Swart2013}.
This fact is a special case of the the Radon-Nikodym theorem, and
$\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
to the counting measure~\cite{Nikodym1930,Folland2013}. For example,
the Radon-Nikodym derivative of $\pmeas$ in example~\ref{ex1} is:
\[
\begin{array}{rcl}
\rho\left(HH\right)=1/3,\quad\rho\left(HT\right)=0,\quad\rho\left(TH\right)=2/3,\quad\rho\left(TT\right)=0\textrm{ .}\end{array}
\]

@@

Actually, constructing a quantum probability measures from a density
matrix~$\rho$ is similar to defining a classical probability measure
by its Radon-Nikodym derivative. This can be seen more easily if we
pick an orthonormal basis~$\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$
such that $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\psi_{j}\in S}}\proj{\psi_{j}}$,
where $S$ is the linear subspace $P$ projects onto. Then, a density
matrix~$\rho$ can also be represented in the same basis, i.e., $\rho=\sum_{i=1}^{d}\sum_{j=1}^{d}r_{ij}\proj{\psi_{j}}$,
and the Born rule becomes
\begin{eqnarray}
\mu_{\rho}^{B}\left(P\right) & = & \Tr\left(\rho P\right)=\sum_{\psi_{j}\in S}r_{jj}\textrm{ ,}\label{BornRule.mixed-1}
\end{eqnarray}
which is basically the same as equation (\ref{eq:Radon-Nikodym}).

The generalized Radon-Nikodym theorem is called Gleason's theorem~\cite{HollandJr1970,Redhead1987-REDINA}
which states that, in Hilbert spaces of dimension $d\geq3$, given
a probability measure $\mu$, there exist a mixed state~$\rho$ that
induces such a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
to the following corollary.

\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$ of dimension
$d\geq3$, for any function~$\mu:\events\rightarrow[0,1]$ satisfying the conditions
listed in lemma~\ref{lem:quantumProbabilityMeasure}, there exist
an unique mixed state~$\rho$ such that $\mu=\mu^B_{\rho}$.\end{cor}

>>>>

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\pr}[2]{\langle #1, #2 \rangle}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ip}[2]{\langle #1 | #2 \rangle}
\newcommand{\proj}[1]{|#1 \rangle\langle #1 |}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}

@@

Although specifying a probability for every event looks complex, a
probability measure can be simply constructed by 
\begin{equation}
\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum\rho(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $\rho:\Omega\rightarrow[0,1]$ and $\tensor*[_{\mathbb{R}}]{\sum}{_{\omega\in\Omega}}\rho(\omega)=1$.
$\rho$ is called the Radon-Nikodym derivative of $\pmeas$ with respect
to the counting measure, and the Radon-Nikodym theorem states that
the converse is also true.

\begin{thm}{[}Radon-Nikodym theorem for finite probability space~\cite{Nikodym1930,Kolmogorov1950,Folland2013,Swart2013}{]}
For every probability measure~$\pmeas$, there exists an unique Radon-Nikodym
derivative~$\rho$ with respect to the counting measure such that
equation (\ref{eq:Radon-Nikodym}) holds.\qed\end{thm}

For example, the Radon-Nikodym derivative of $\pmeas$ in example~\ref{ex1}
is: 
\[
\begin{array}{rcl}
\rho\left(HH\right)=1/3,\quad\rho\left(HT\right)=0,\quad\rho\left(TH\right)=2/3,\quad\rho\left(TT\right)=0\textrm{ .}\end{array}
\]

@@

Recall that the Radon-Nikodym theorem claims every probability measure
has an unique Radon-Nikodym derivative with respect to the counting
measure. When we generalize the Radon-Nikodym theorem to quantum,
the mixed state~$\rho$ can be considered as the Radon-Nikodym derivative
with respect to the trace~\cite{HollandJr1970,Redhead1987-REDINA,Jaeger2007},
and gives Gleason's theorem: in Hilbert spaces of dimension $d\geq3$,
given a quantum probability measure $\mu$, there exist a mixed state~$\rho$
that induces such a measure using the Born rule~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
By applying Gleason's theorem, we can extend lemma~\ref{lem:quantumProbabilityMeasure}
to the following corollary.

\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$ of
dimension $d\geq3$, for any function~$\mu:\events\rightarrow[0,1]$
satisfying the conditions listed in lemma~\ref{lem:quantumProbabilityMeasure},
there exists an unique mixed state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.\end{cor}
